Topics Causal Inference

### 2024-08-14 documents/paper.tex
Add section on software; add WGAN results.

\subsection{Generic Machine Learning}
The generic ML approach allows want to place as little assumptions as possible on the data generating process, while maintaining valid inference.
This is achieved by (a) moving the inferential target to \textit{features} of the CATE (like the BLP) and (b) using sample splitting to derive inferential guarantees.
Hence, this comes at the cost of potentially being able to only make statements about a (bad) approximation to the original inferential target as well as a loss in precision due to sample splitting.
However, there are a number of clear advantages: The researcher does not have to commit to a specific --- small --- set of covariates ex-ante or make sparsity assumptions.
At the same time, the approach as discussed in \cite{chernozhukov2023genml} does not allow for nuisance parameter estimation, i.e.\ requires a known propensity score.

@@

>>>>

\subsection{Generic Machine Learning}
The generic ML approach allows want to place as little assumptions as possible on the data generating process, while maintaining valid inference.
This is achieved by (a) moving the inferential target to \textit{features} of the CATE (like the BLP) and (b) using sample splitting to derive inferential guarantees.
Hence, this comes at the cost of potentially being able to only make statements about a (bad) approximation to the original inferential target as well as a loss in precision due to sample splitting.
However, there are a number of clear advantages: The researcher does not have to commit to a specific --- small --- set of covariates ex-ante or make sparsity assumptions.
At the same time, the approach as discussed in~\cite{chernozhukov2023genml} does not allow for nuisance parameter estimation, i.e.\ requires a known propensity score.

@@

\subsection{Software Packages}
For the baseline causal forest estimator I rely on the `CausalForest' implementation provided by the \href{https://econml.azurewebsites.net/}{EconML} Python package.
This package implements a range of machine learning techniques for causal based on the statistical literature and making use of existing machine learning implementations in Python.
For the generic ML part, I implemented most algorithms by hand since these only involve specifying linear regressions and sample splitting.
Again, it is possible to flexibly use any of the machine learning estimators in this case, for example implemented in EconML or sklearn directly.
For estimating DGPs using Wasserstein Generative Adversarial Networks (WGAN) I use the \href{https://github.com/gsbDBI/ds-wgan}{ds-wgan} implementation provided by the authors.
Unfortunately, the code is not maintained and not compatible with recent versions of most basic Python libraries (e.g. NumPy 2.0).
To avoid dependency conflicts with the other packages or manually debugging their code, I instead trained the generators in a Google Colab environment, which also comes at a significant speedup due to GPU availability.
